\section{Background}

This section makes a brief introduction to ProActive \cite{huet04high}, the basic computing framework our solution extends.

\subsection{ProActive}

ProActive Parallel Suite developed by French national laboratory INRIA, is an innovative open-source solution for acceleration of applications. It is seamlessly integrated with the management of high-performance clouds, and simplifies the parallel program development in cluster, grid and cloud computing environment. ProActive is completely based on Java development for parallel distributed computing, and does not make any modification on Java Virtual Machine (JVM), so it can run on any operating system which supports a standard Java environment. With a ProActive platform, the users tackle the acceleration and orchestration of all demanding applications easily. %\cite

To execute parallel tasks in distributed environments, such as clouds and clusters, requires a unified mechanism for scheduling tasks and managing resources, and the original ProActive is equipped with a batch scheduler. %\cite
The scheduler provides an abstraction of resources for users. It allows users to submit jobs, containing one or several tasks, and then to execute these tasks on available resources. It enables several users to share the same resource pool and also to tackle the problem involved with distributed environment, like failing tasks or resources. It also allows users to kill a specified task easily, and start the task again in another node.

By default, the scheduler assigns tasks according to the default FIFO (First In First Out) priority policy. If a task needs to be scheduled quickly, the user can increase its priority, or change such basic policy. In ProActive, to create and add a new scheduling policy is very simply. The users only need to implement the policy interface, and execute the scheduler with the new policy as argument.

The ProActive Scheduler \cite{pascheduling} is connected to a Resource Manager \cite{parm} providing therefore the resource abstraction. The Resource Manager is a component for resource aggregation across the network. It sends compute units represented by ProActive nodes (Java Virtual Machines running the ProActive Runtime)   to the scheduler which manages the task workflow and distributed tasks on accessible resources. According to the deployment, it can retrieve the computing nodes using different standard such as SSH, LSF, OAR, gLite, EC2, etc.

Including Scheduler, Resource Manager and other components, the ProActive platform can thus easily run on a cluster, a grid or a cloud or any mixture of them without modification, and get better performance for high performance and distributed computing.

\subsection{Outliers}

Many previous works have identified outliers as a critical performance killer in heterogeneous clouds. Even in high end clusters, outliers are still an issue. Take our experimental cluster for example. We share this large local cluster, which has 8800 CPU cores over 740 server nodes, with many other institutes and researchers. As the local cluster is mainly build for scientific computing, it only provides a Load Shared Facility (LSF) job scheduling system for users to submit jobs in parallel. This situation is similar to what happens in the cloud, where many virtual machines share some physical servers.

Additionally, we have another small cluster that is dedicated to our experiment. To better utilize both parts of computational resources, we deployed a uniform ProActive Scheduling System to administrate all available resources. Based on the ProActive platform, we successfully extend the flexibility of using large-scale clusters. In such a heterogeneous environment, outliers often emerge.

The traditional ProActive global scheduler does not support collaboration and communication with the local job scheduler on a cluster, so that too much CPU contention on some node leads to outliers. The outliers prolong the completion time of job and harm the performance of ProActive seriously.
